Combined Task and Motion Planner through an Interface Layer

### 2015-04-18 documentation/draft.tex

In order to achieve high level goals a robot must combine task and motion planning. 
A robot uses task planning to determine its long term strategy and motion planning to determine the movements movements it  will execute to achieve the task. 
Effectively combining task and motion planning is an open research problem. 
We developed an interface between the motion and task planning. 
Our system uses off-the-shelf task and motion planners and makes no assumptions about their implementation.

@@

The main contribution of this implementation is an interface layer.  
This interface layer is designed to be planner-independent: that is, it can work with any motion planner and task planner, so long as the outputs from each are conformed to the interface specified by the API.  
The interface layer interleaves calls between the task planner and the motion planner, using geometric feasibility determined through the motion planner to affect the state given to the task planner to plan from.

@@

Specifically, the interface layer starts by generating a high level plan and attempting to generate motion plans corresponding to each action.  
When it's not possible to generate a motion plan, the interface layer determines what geometric constraints are causing the problem and relays this back to the task planner in an appropriate format.  
Then, the task planner replans from that set state and the process continues.  
When necessary, backtracking occurs.

In order to communicate with the task planner and motion planner, the interface layer utilizes ROS services.  
For the task planner, the interface layer instantiates a server with a given PDDL domain file.  
This domain file specifies the different actions that are feasible along with their preconditions and postconditions.  
For individual service calls, the interface layer takes an internal `state' variable, converts it to PDDL format, and sends it to the server to be solved.  
The task planner service responds with a high level plan or a notification that finding a plan failed.  
If finding a plan failed, the interface layer begins backtracking.  
If a high level plan is found, the interface layer begins searching for refinements of each action as a motion plan.

For the motion planner, the interface layer again communicates via a ROS service.  
The motion planner is given an action, a world state, and a pose or set of poses corresponding to sub-parts of the action.  
If it is possible to perform the action using the intermediary poses specified, the motion plan returns the trajectory.  
If not, it returns an error message.

If the motion plan does not succeed, a variety of poses are tried.  
Poses are generated randomly from a pose generator.  
If no poses are successful, the interface layer determines what is blocking the motion plan from succeeding.  
Specifically, it removes objects from the environment until a feasible motion plan is found.  
If still no feasible motion plan is found, backtracking is required.  
If a feasible motion plan is found with some subset of objects removed, then that information is relayed back to the task planner.  
The task planner replans from the step where we failed to find a motion plan.  
At that state, we add in predicates corresponding to the object obstructions.  
Then, the task planner replans from there.

@@

Veronica: probably should fix this to be a nice alignment environment within LaTeX
$PICKUP(obj_1, gripper, pose_1, pose_2, traj)$

@@

@@

$EMPTY(gripper)$ -- this specifies whether the gripper is empty and thus available to hold a block.

$ROBOTAT(pose_1)$ -- this specifies where the robot is.  $pose_1$ is a symbolic reference to a continuous variable.

$ISGPFG(pose, obj)$ -- this specifies whether a pose is a Gripper Pose For Grasping (GPFG) an object.

$ISMP(traj, pose_1, pose_2)$ -- this specifies whether a trajectory is a motion plan from one pose to another.

$OBSTRUCTS(obj_1, traj, obj_2)$ -- this specifies whether an object blocks another object from being picked up along a trajectory.

$PDOBSTRUCTS(obj_1, traj, obj_2, tloc)$ -- this specifies whether an object blocks another object from being put down at a particular location along a trajectory.

$IN(obj_1, gripper)$ -- this specifies whether an object is currently grasped by the gripper.

@@

The most important limitation of this implementation is to remember that it is an interface layer.  
It does not include a task planner and a motion planner: you must set those up yourself as ROS services and make sure that the output and input message types specify those outlined in the API.  
Depending on what planners you use, setting them up and installing them may be nontrivial.  
Different planners are effective for different tasks and some planners may require extensive installation.  
When you pick your task and motion planners, remember that this interface layer is set up to only work with task planners that use the PDDL specification language.  
If you choose to use another specification system, you will need to translate between PDDL and your system.

On a more detailed level, it is important to note that this planner is not guaranteed to find an optimal solution, or even to find a solution at all.  
We refer you to [1] for a proof that this algorithm is guaranteed to find a solution for problems with certain properties.  
However, due to the random nature of the pose generators and that there are limits set on the number of iterations, a valid plan may not be found for all problems.

>>>>

In order to achieve high level goals a robot must combine task and motion planning. 
A robot uses task planning to determine its long term strategy and motion planning to determine the movements it  will execute to achieve the task. 
Effectively combining task and motion planning is an open research problem. 
We implemented an interface between the motion and task planning. 
Our system uses off-the-shelf task and motion planners and makes few assumptions about their implementation.

@@

The main contribution of this implementation is an interface layer.  
This interface layer is designed to be planner-independent: that is, it can work with any motion planner and task planner, so long as the outputs from each are conformed to the interface specification.  
The interface layer interleaves calls between the task planner and the motion planner, using geometric feasibility determined through the motion planner to affect the state given to the task planner to plan from.

@@

The interface layer starts by asking the task planner to generate a high level plan and has the motion planner instaniate motion plans corresponding to each action.  
When it's not possible to generate a motion plan, the interface layer determines what geometric constraints are causing the problem and relays this back to the task planner.  
Then, the task planner replans from that state and the process continues.  
When necessary, backtracking occurs.

At start time, the task planner is given a PDDL domain specifying the different actions that are feasible along with their preconditions and postconditions.  
For individual calls to the task planner, the interface layer takes an internal `state' variable, converts it to PDDL format, and sends it along to be solved.  
The task planner responds with a high level plan or a notification that finding a plan failed.  
If finding a plan failed, the interface layer begins backtracking.  
If a high level plan is found, the interface layer begins searching for refinements of each action as a motion plan.

On each call to the motion planner, the interface layer provides the motion planner with the intended action, the world state, and a pose or set of poses  
corresponding to sub-parts of the action. These poses are randomly generated for each action by a pose generator within the interface layer. 
If it is possible to perform the action using the intermediary poses specified, the motion plan returns the trajectory and the updated world state.  
If not, it returns an error message.

If the motion plan does not succeed, a variety of poses are tried.  
Again, poses are generated randomly from a pose generator.  
If no poses are successful, the interface layer determines what is blocking the motion plan from succeeding by removing objects from the environment until a feasible motion plan is found.  
If still no feasible motion plan is found, backtracking is required.  
If a feasible motion plan is found with some subset of objects removed, then that information is relayed back to the task planner after the PDDL state is appropriatedly updated.
This update adds predicates corresponding to the object obstructions, and the task planner is asked to replan starting from the step where we failed to find a motion plan. This whole process continues until a feasible motion plan has been found.

@@

\vspace{10}
$PICKUP(obj_1, gripper, pose_1, pose_2, traj)$

@@

\vspace{10}

@@

\vspace{10}

$EMPTY(gripper)$ -- gripper is empty and thus available to hold a block.

$ROBOTAT(pose_1)$ -- robot pose,  $pose_1$ is a symbolic reference to a continuous variable.

$ISGPFG(pose, obj)$ -- $pose$ is a Gripper Pose For Grasping (GPFG) an object $obj$.

$ISMP(traj, pose_1, pose_2)$ -- $traj$ is a motion plan from $pose_1$ to $pose_2$.

$OBSTRUCTS(obj_1, traj, obj_2)$ -- $obj_1$ blocks $obj_2$ from being picked up along $traj$.

$PDOBSTRUCTS(obj_1, traj, obj_2, tloc)$ -- $obj_1$ blocks $obj_2$ from placement at $tloc$ along $traj$.

$IN(obj_1, gripper)$ -- $obj_1$ currently grasped by $gripper$.

\vspace{10}

@@

It is important to note that this planner is not guaranteed to find an optimal solution, or even to find a solution at all.  
We refer you to [1] for a proof that this algorithm is guaranteed to find a solution for problems with certain properties.  
However, due to the random nature of the pose generators and that there are limits set on the number of iterations, a valid plan may not be found for all problems.
